Title here

### 2016-09-27 portfolio/text/anderson-etal-rev-pfx.tex
Narrow down draft titles
Incorporate Jordan's suggestions

\title{Portfolios of fishing permits and species
reduce risk but adjusting fishing strategy is risky}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson
}

@@

>>>>

\title{Benefits of diversification and risks of changing strategies for individual fishers\\
Benefits of diversification are unavailable to many fishermen\\
}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson$^X$,
\ldots
}

\newlabel{tab:strategies}{1}
\newlabel{fig:fe}{1}
\newlabel{fig:re}{2}
\newlabel{fig:spoke-all}{3}
\newlabel{fig:resid}{4}
\newlabel{fig:resid-downside}{5}
\newlabel{fig:str-yrs}{6}

@@

\noindent
$^X$Ted Stevens Marine Research Institute, Alaska Fisheries Science Center, 17109
Pt Lena Loop Road, Juneau, AK 99801, USA

### 2016-09-27 portfolio/text/ms.Rmd
Incorporate Jordan's suggestions

\noindent
where $s$ indexes species from $1$ through $n$.
We calculated effort or effective season length as
the sum the season lengths for each permit each year.
Season length for a given permit
was calculated as the the number of days between
the first instance of fishing a permit
and the last instance of fishing a permit each year.
For example, if someone fished for 30 days
on a salmon drift gillnet permit in Southeast Alaska
and 40 days on a statewide longline halibut permit,
that individual's season length
would be 70 days.

@@

We use $\log(R_{i,t-1}$) as an offset, and thus
our model describes the percent change in revenue,
i.e., $\log(R_{i,t}) - \log(R_{i,t-1}) = \log(R_{i,t}/R_{i,t-1})$.
We model change in revenue because preliminary analysis revealed non-stationary trends in
revenue (resulting from experience or other unmodeled factors). This approach required filtering the data
to remove person-year combinations without a subsequent year of revenue, but
presents a number of advantages:
it eliminates having to deal with the non-stationary
time series and eliminates having to
estimate thousands of intercepts associated individual fishers.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability2.pdf}
\caption{Individuals who fish
permits and permit combinations (permit strategies) with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common permit strategies.
Thick black line, and dark and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strategy-level regression built into the hierarchical model.
Estimated variability represents expected standard deviation
for a permit holder who does not change
species diversity or days fished from year to year
with the strategy-level effect of mean days fished removed.
}
\label{fig:across}
\end{center}
\end{figure}

>>>>

\noindent
where $s$ indexes species from $1$ through $n$.
We calculated effort or effective season length as
the sum of the season lengths for each permit each year.
Season length for a given permit
was calculated as the the number of days between
the first instance of fishing a permit
and the last instance of fishing a permit each year.
For example, if someone fished for 30 days
on a salmon drift gillnet permit in Southeast Alaska
and 40 days on a statewide longline halibut permit,
that individual's season length
would be 70 days.

@@

We use $\log(R_{i,t-1}$) as an offset, and thus
our model describes the percent change in revenue,
i.e., $\log(R_{i,t}) - \log(R_{i,t-1}) = \log(R_{i,t}/R_{i,t-1})$.
We model change in revenue because preliminary analysis 
revealed non-stationary trends in
revenue (resulting from experience or other unmodeled factors). 
This approach eliminates having to deal with the non-stationary
time series and eliminates having to
estimate thousands of mean-revenue intercepts 
associated with individual fishers.
We removed person-year combinations without a subsequent year of revenue.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability2.pdf}
\caption{Individuals who fish
permits and permit combinations (permit strategies) with higher species diversity
have lower expected revenue variability.
On the y-axis, dots, thick lines, and thin lines represent posterior medians,
50\%, and 95\% credible intervals for
the `r nstr` most common permit strategies.
Thick black line, and dark and light grey shaded regions
indicate median, 50\%, and 95\% credible intervals
of strategy-level regression built into the hierarchical model.
Estimated variability represents expected standard deviation
for a permit holder who does not change
species diversity or days fished from year to year.
}
\label{fig:across}
\end{center}
\end{figure}
